Articles of Association of London Hackspace Ltd.

### 2011-06-01 constitution/articles-body.tex
Use the description environment (still looks a bit tatty...)

\item
  In the articles:
  \begin{itemize}
  \item
    ``address'' means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the charity;
  \item
    ``the articles'' means the charity's articles of association;
  \item
    ``the charity'' means the company intended to be regulated by the
    articles;
  \item
    ``clear days'' in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect;
    \end{itemize}
  \item
    ``the Commission'' means the Charity Commission for England and
    Wales;
  \item
    ``Companies Acts'' means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the charity;
  \item
    ``the directors'' means the directors of the charity. The directors
    are charity trustees as defined by section 97 of the Charities Act
    1993;
  \item
    ``document'' includes, unless otherwise specified, any document
    sent or supplied in electronic form;
  \item
    ``electronic form'' has the meaning given in section 1168 of
    theCompanies Act 2006;
  \item
    ``the memorandum'' means the charity's memorandum of association;
  \item
    ``officers'' includes the directors and the secretary (if any);
  \item
    ``the seal'' means the common seal of the charity if it has one;
  \item
    ``secretary'' means any person appointed to perform the duties of
    the secretary of the charity;
  \item
    ``the United Kingdom'' means Great Britain and Northern Ireland;
    and
  \item
    words importing one gender shall include all genders, and the
    singular includes the plural and vice versa.
  \end{itemize}
  Unless the context otherwise requires words or expressions
  contained in the articles have the same meaning as in the Companies
  Acts but excluding any statutory modification not in force when
  this constitution becomes binding on the charity.

>>>>

\item
  In the articles:
  \begin{description}
  \item[Address] means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the charity
  \item[The Articles] means the charity's articles of association
  \item[The Charity] means the company intended to be regulated by the
    articles
  \item[Clear days] in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect
    \end{itemize}
  \item[The Commission] means the Charity Commission for England and Wales
  \item[Companies Acts] means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the charity
  \item[The Directors] means the directors of the charity. The directors
    are charity trustees as defined by section 97 of the Charities Act
    1993
  \item[Document] includes, unless otherwise specified, any document
    sent or supplied in electronic form
  \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
  \item[The Memorandum] means the charity's memorandum of association
  \item[Officers] includes the directors and the secretary (if any)
  \item[The seal] means the common seal of the charity if it has one
  \item[Secretary] means any person appointed to perform the duties of
    the secretary of the charity
  \item[The United Kingdom] means Great Britain and Northern Ireland.
  \end{description}
  Words importing one gender shall include all genders, and the singular
  includes the plural and vice versa.

  Unless the context otherwise requires words or expressions
  contained in the articles have the same meaning as in the Companies
  Acts but excluding any statutory modification not in force when
  this constitution becomes binding on the charity.
